STA610 Case Study 1 Team 4 Report

### 2021-03-21 Draft Report 3.21.Rmd
updated the random effect results

#### Random Effects
```{r}
#VarCorr(mod1)
Variance <- c(0.04748, 0.96369)
Std.Dev <- c(0.2179, 0.9817)
Groups <- c("state (Intercept)", "Residual")

@@

knitr::kable(REvar, col.names = c("Group", "Variance", "Std.Dev"))
```
The within-state variance $\sigma^2$ is 0.96369, which is much larger than the across-state variance $\tau^2$, 0.04748.

@@

```{r, fig.align='center', fig.height=8}
dotplot(ranef(mod_final, condVar=TRUE))$state
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Nevada is the lowest and this intercept is also significant.

>>>>

#### Random Effects
```{r}
#VarCorr(mod1)
Variance <- c(0.0233, 0.5028)
Std.Dev <- c(0.1526, 0.7091)
Groups <- c("state (Intercept)", "Residual")

@@

knitr::kable(REvar, col.names = c("Group", "Variance", "Std.Dev"))
```
The within-state variance $\sigma^2$ is 0.5028, which is much larger than the across-state variance $\tau^2$, 0.0233.

@@

```{r, fig.align='center', fig.height=8}
dotplot(ranef(mod_final, condVar=TRUE))$state
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Arizona is the lowest and this intercept is also significant.
